Succinct representations for abstract interpretation

### 2011-11-02 papers/PLDI2012/implicitization.tex
+rq sur anonymat
subtitle
Oops, une remarque qui était mal placée
mise en forme de 'g' et fix commentaire
ajout de 0 devant les . dans les tableaux

\title{Succinct representations for abstract interpretation}
%\subtitle{Subtitle Text, if any}

@@

\begin{eqnarray*}
g(p_i) = & \rho \wedge b_i^s \wedge 
\displaystyle\bigwedge_{j \in P_R \atop j \neq i} \neg b_j^s  \\
 & \wedge 
\displaystyle\bigvee_{1 \leq k \leq m_i} (d_k \wedge X_{i,k} \wedge \bigwedge_{l \neq k}
\neg d_l) \\
 & \wedge
\displaystyle\bigvee_{j \in Succ(i)} 
(b_j^d \wedge \bigwedge_{1 \leq k \leq m_i} (\neg X_{j,k}))
\end{eqnarray*}

@@

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}

\MM{Et que prend-t-on pour $\delta$ ? C'est 1 tout le temps ?}

@@

\MM{On peut peut-être citer le nom de l'outil (on garde PAGAI ?) ici.
  L'intérêt d'avoir un nom, c'est que les gens peuvent en parler plus
  facilement, et c'est plus facile de retrouver le papier origine d'un
  outil quand il cite son nom}

@@

\begin{figure}[h]
  \MM{Je trouve que les zéro-virgule-quelque-chose comme .17 font
    moches à côté des zéros, vu que les tableaux sont alignés sur le
    ., les ``0'' sont tout à gauche et les ``.17'' tout à droite. Je
    vote pour des 0.17 pour que l'alignement soit bon, ça rendrait la
    lecture plus facile je trouve}
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants stronger with the right-side technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
\end {figure}

>>>>

\title{Succinct representations for abstract interpretation}
\subtitle{Combined analysis algorithms and experimental evaluation}

@@

\begin{eqnarray*}
g(p_i) & = & \rho \wedge b_i^s \wedge 
\displaystyle\bigwedge_{j \in P_R \atop j \neq i} \neg b_j^s  \\
 & & \wedge 
\displaystyle\bigvee_{1 \leq k \leq m_i} (d_k \wedge X_{i,k} \wedge \bigwedge_{l \neq k}
\neg d_l) \\
 & & \wedge
\displaystyle\bigvee_{j \in Succ(i)} 
(b_j^d \wedge \bigwedge_{1 \leq k \leq m_i} (\neg X_{j,k}))
\end{eqnarray*}

@@

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$. We also define $\delta_i = 1$ for each $i, p_i \in
P_R$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}

@@

\MM{On peut peut-être citer le nom de l'outil (on garde PAGAI ?) ici.
  L'intérêt d'avoir un nom, c'est que les gens peuvent en parler plus
  facilement, et c'est plus facile de retrouver le papier origine d'un
  outil quand il cite son nom}
\DM{Dans la version finale, oui, mais pas dans une soumission anonymisée... suffit de Googlifier pagai sur imag.fr}

@@

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants stronger with the right-side technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
\end {figure}
